Loop Device Performance Overhead for Constraining Batch Job Tasks:\\A Technical Report and Experiment in Metascience

### 2016-06-24 paper.tex
Fixes some grammar and sentence structure

\subsection{Allocation}
To allocate a loop device, one must first create a file filled with arbitrary data up to a specified size. This is accomplished by executing a command like {\tt{dd}} in Linux systems. Following the creation of this file, it is bound to an available loop device using the {\tt{losetup}} Linux comand. The operating system of our test platform has eight available loop devices by default with the option to allow up to 256. This allows for 256 resource constrained tasks to run concurrently. Following this step, a new filesystem is instantiated on the loop device. Finally, the loop device is mounted, after which it is ready for I/O.

\subsection{Deallocation}
The deallocation of a loop device is simpler than its setup. First, one must unmount the loop device via the invocation of the {\tt{umount}} command. Then the file used as the mountpoint is unbound from its associated loop device. The file is once again visible to the native filesystem and is removed.

\subsection{Library Implementation}
We have simplified the allocation and deallocation of loop devices with the creation of a new library consisting of two functions, {\tt{disk\_alloc\_create}} and {\tt{disk\_alloc\_delete}} which handle the creation and deletion of a loop device respectively. This library is implemented in the CCTools software suite within the Work Queue batch system and the Makeflow workflow management system.

@@

\subsection{Performance}
The results presented in Figures \ref{fig:2gb}, \ref{fig:4gb}, and \ref{fig:8gb} display the median value across each nest depth with the respective median absolute deviation. This format was chosen in order to present the most accurate representation of loop device performance. The performance of a loop device mounted with the any of the ext family filesystems performs comparably in many cases with the native filesystem. The native filesystem of our test platform is ext4. By using non-trivial sizes for the test allocations (in the order of GBs), our micro-benchmarks simulate sustained I/O expected of a batch job task completing a realistic work load. This is opposed to burst I/O which would be seen in tasks smaller than 1GB.

>>>>

\subsection{Allocation}
To allocate a loop device, we first create a file filled with arbitrary data up to a specified size. This is accomplished by executing a command like {\tt{dd}} in Linux systems. Following the creation of this file, it is bound to an available loop device using the {\tt{losetup}} Linux comand. The operating system of our test platform has eight available loop devices by default with the option to allow up to 256. This allows for 256 resource constrained tasks to run concurrently. Following this step, a new filesystem is instantiated on the loop device. Finally, the loop device is mounted, after which it is ready for I/O.

\subsection{Deallocation}
The deallocation of a loop device is simpler than its setup. First, we unmount the loop device via the invocation of the {\tt{umount}} command. Then the file used as the mountpoint is unbound from its associated loop device. The file is once again visible to the native filesystem and is removed.

\subsection{Library Implementation}
We have simplified the allocation and deallocation of loop devices with the creation of a new library consisting of two functions, {\tt{disk\_alloc\_create}} and {\tt{disk\_alloc\_delete}}, which handle the creation and deletion of a loop device respectively. This library is implemented in the CCTools software suite within the Work Queue batch system and the Makeflow workflow management system.

@@

\subsection{Performance}
The results presented in Figures \ref{fig:2gb}, \ref{fig:4gb}, and \ref{fig:8gb} display the median value across each nest depth with the respective median absolute deviation. This format was chosen in order to present the most accurate representation of loop device performance. The performance of a loop device mounted with any of the ext family filesystems performs comparably in many cases with the native filesystem. The native filesystem of our test platform is ext4. By using non-trivial sizes for the test allocations (in the order of GBs), our micro-benchmarks simulate sustained I/O expected of a batch job task completing a realistic work load. This is opposed to burst I/O which would be seen in tasks smaller than 1GB.
